Modelling BCG vaccination in the UK

### 2019-12-16 rmds/07-direct-effect-bcg-change.Rmd
finalised model dev equation changes

```{r 07-inc-rate-summary-plot, fig.cap = "Incidence rates (with 95% confidence intervals) per 100,000 per year for UK born population and non-UK born population, aged 0-5 and therefore directly affected by the targeted neonatal vaccination programme, and aged 14-19 and therefore directly affected by the universal school-age scheme."}
knitr::include_graphics("chapters/direct-eff-bcg-change/figure-2.png")
```

>>>>

```{r 07-inc-rate-summary-plot, fig.cap = "Incidence rates (with 95\\% confidence intervals) per 100,000 per year for UK born population and non-UK born population, aged 0-5 and therefore directly affected by the targeted neonatal vaccination programme, and aged 14-19 and therefore directly affected by the universal school-age scheme."}
knitr::include_graphics("chapters/direct-eff-bcg-change/figure-2.png")
```

### 2019-12-16 rmds/08-model-development.Rmd
finalised model dev equation changes

The model presented in this chapter is not the first dynamic model of TB transmission in England to be developed nor is it the first model including BCG vaccination. Vynnycky et al. developed a highly detailed - and rigorously parameterised - model of TB transmission in England and Wales.[@Vynnycky1997a] However, unlike the model presented in this chapter, this model only included the white male population, it only modelled transmission until 1990, and it did not capture the full complexity of BCG vaccination. Harris et al. reviewed TB models that explored the impact of potential future vaccines.[@Harris2016] They found that model structures evolved over time, with only a few models including the variable infectiousness of active disease, vaccine waning, and age stratification - all of which are included in the model presented in this chapter. Few of the models they evaluated considered low incidence settings, like England. The model presented in this chapter also makes use of recent advances in TB modelling that indicate which features are key to reproducing TB transmission dynamics.[@Ragonnet2017; @Brooks-Pollock2010] Several previous studies have evaluated the role of BCG vaccination and considered various different vaccination scenarios.[@Manissero2008a; @Trunz2006; @Rahman2001a; @Usher2016; @Bhunu2008b] However, these studies either did not consider TB transmission or made use of simple transmission models that did not capture the full complexity of either TB transmission of BCG vaccination. Finally, the model presented in this chapter makes use of a highly detailed routine surveillance data set to provide setting appropriate prior distributions for key parameters that were not available for previous models. For further details of previous modelling approaches and their strengths and weaknesses in comparison to the model presented here please see the Discussion section of this chapter.

>>>>

The model presented in this chapter is not the first dynamic model of TB transmission in England to be developed nor is it the first model including BCG vaccination. Vynnycky et al. developed a highly detailed - and rigorously parameterised - model of TB transmission in England and Wales.[@Vynnycky1997a] However, unlike the model presented in this chapter, this model only included the white male population, it only modelled transmission until 1990, and it did not capture the full complexity of BCG vaccination. Harris et al. reviewed TB models that explored the impact of potential future vaccines.[@Harris2016] They found that model structures evolved over time, with only a few models including the variable infectiousness of active disease, vaccine waning, and age stratification - all of which are included in the model presented in this chapter. Few of the models they evaluated considered low incidence settings, like England. The model presented in this chapter also makes use of recent advances in TB modelling that indicate which features are key to reproducing TB transmission dynamics.[@Ragonnet2017; @Brooks-Pollock2010] Several previous studies have evaluated the role of BCG vaccination and considered various different vaccination scenarios.[@Manissero2008a; @Trunz2006; @Rahman2001a; @Usher2016; @Bhunu2008b] However, these studies either did not consider TB transmission or made use of simple transmission models that did not capture the full complexity of either TB transmission or BCG vaccination. Finally, the model presented in this chapter makes use of a highly detailed routine surveillance data set to provide setting appropriate prior distributions for key parameters that were not available for previous models. For further details of previous modelling approaches and their strengths and weaknesses in comparison to the model presented here please see the discussion section of this chapter.
